---
title: "Scenario"
author: "Camilla Novaglio"
date: "05/11/2019"
output: html_document
---

#-----------------------------------------
# upload codes and data 
#----------------------------------------------

```{r}

# trial 

rm(list=ls())

library(tidyverse)
library(devtools)
library(plyr) 
library(Rcpp) # this will allow you to run the inner_project_loop 
library(reshape2)
library(inline)
library(ggplot2)
library(vegan)
# install.packages("shiny")
# library(mizer) # if inner_loop error, you need to upload mizer
library(shiny)
library("purrr")
library("dplyr")

setwd("/Users/nov017/R-projects/Mizer-fleet/R")
source("data.R") 
source("help.R") 
source("MizerParams-class.R") 
source("MizerSim-class.R")
source("plots.R")
source("project_methods.R")
source("project.R")
source("RcppExports.R") 
source("selectivity_funcs.R")
source("summary_methods.R")
source("wrapper_functions.R")
source("DataFunction.R") 

# load data 
# load("/Users/nov017/Dropbox/Mizer-fleet/R/model/FDData_Nov.RData") # FDData_opn3.RData or FDData_opn2.RData (was FDData_Nov.RData)
# new folder
load("/Users/nov017/Dropbox/Mizer-fleet_extension/data/FDData_opn3_May.RData")

# not sure I should specify this here?
sim = sim_FD_bmsy
df_param = df_param2
interaction = theta
kappa = kappa
kappa_ben = kappa_ben
kappa_alg = kappa_alg
w_pp_cutoff = w_pp_cutoff
min_w_bb = min_w_bb
w_bb_cutoff = w_bb_cutoff
fleetDynamics = TRUE
selectivity_params = df_selParam_new
catchability = df_target_bmsy2
target = df_target_bmsy2
effort = 0
dt = 0.25
management = TRUE
price = df_price_new
cost = df_cost3
diet_steps = 0
ke = ke_fleet
scaling_price = scaling_price
Blevel_management = "Bmsy"
initial_n = initial_n
initial_n_pp = initial_n_pp
initial_n_bb = initial_n_bb
initial_effort = initial_effort2

```

#-----------------------------------------
# fleet strucutres and scenarios
#----------------------------------------------

```{r}
######## Scenario: initial caommunity as per last time step of time-variant community. Run forward using price and costs as per last time step of time-variant community, but changing interaction matrix as per scenarios. 

####### initial community
initial_n_scenario = sim@n[nrow(sim@n),,]
initial_n_pp_scenario  = sim@n_pp[nrow(sim@n_pp),]
initial_n_bb_scenario  = sim@n_bb[nrow(sim@n_bb),]
initial_effort_scenario = sim@effortOut[dim(sim@effortOut)[1],]   

####### forward price and costs
t_max = 13 # till 2030 or 2050? if you run it for too long it's going to collaps... 
price_forward = t(replicate(t_max, price[nrow(price),]))
rownames(price_forward)<-seq(1:t_max) # or...
rownames(price_forward)<-seq(2018,(2018+t_max-1))

cost_forward1 <- t(replicate(t_max, cost[nrow(cost),,1]))
rownames(cost_forward1)<-seq(1:t_max) # or ... 
rownames(cost_forward1)<-seq(2018,(2018+t_max-1))

cost_forward2 <- t(replicate(t_max, cost[nrow(cost),,2]))
rownames(cost_forward2)<-seq(1:t_max) # or ...
rownames(cost_forward2)<-seq(2018,(2018+t_max-1))

cost_forward <-array(c(cost_forward1,cost_forward2), dim = c(t_max,dim(cost)[2],dim(cost)[3])) # or ...
cost_forward <-array(c(cost_forward1,cost_forward2),dim = c(dim(cost_forward1)[1],dim(cost)[2],dim(cost)[3]), dimnames = c(dimnames(cost_forward1)[1],dimnames(cost)[2],dimnames(cost)[3]))

####### TRIAL changes in Bmsy fro platy and genypt - this is done in SEAmodel if you decide to go this way
df_param2<-df_param
# df_param2[9, "Bmsy"]<-0 #df_param2[9, "Bmsy"]*0.001 
# df_param2[16, "Bmsy"]<-0 #df_param2[16, "Bmsy"]*0.0001 




####### interaction matrix options

######## note - be carefull with these values, does this mean that exploitation rate is higher than 1? the values below act as catchability only, but if you add all the Fmort from all the fleets? check that exploitation rate (catch/biomass at t) is lower than 1 

# colSums(df_target_bmsy2*initial_effort2)
# 
# # or model output... 
# 
# a<-getBiomass(sim)
# b<-sim@yield
# b<-rowSums(aperm(b,c(1,2,4,3)),dims=3) # sum over size
# b<-rowSums(b,dims=2)
# c<-b/a
# c[c>0.2] # exploitation rate for all spp is less than 20%

######## trial model to understand things - status quo (initial community and fleets as per sim_FD_bmsy)

params_trial <- MizerParams(df_param2, interaction = theta, kappa = kappa, kappa_ben = kappa_ben, kappa_alg = kappa_alg, w_pp_cutoff = w_pp_cutoff, min_w_bb = min_w_bb, w_bb_cutoff = w_bb_cutoff, fleetDynamics=TRUE, selectivity_params = selectivity_params, catchability = catchability, target = target)
 
sim_trial <- project(params_trial, effort = 0, dt = dt, fleetDynamics = TRUE, management = TRUE, multiFleet = FALSE, price = price_forward, cost = cost_forward, diet_steps = 0, ke = ke, initial_effort = initial_effort_scenario, scaling_price = scaling_price, Blevel_management = Blevel_management, initial_n = initial_n_scenario, initial_n_pp = initial_n_pp_scenario , initial_n_bb = initial_n_bb_scenario )

plotFleet(sim_trial)
# plotBiomass(sim_trial)$plot + facet_wrap(~Species)
# plot_CN(sim)
# plotFleet(sim)




# try understand 
# 1 why effort = 0 even if less than 5 spp are below 20? becasue 0s are due to plety being below 40 and the main catch, also some decreases are due to profits; 
# 2 why effort = 0 for less than 4 years before becoming 0.01... seems OK now...

# params_trial <- MizerParams(df_param2, interaction = theta, kappa = kappa, kappa_ben = kappa_ben, kappa_alg = kappa_alg, w_pp_cutoff = w_pp_cutoff, min_w_bb = min_w_bb, w_bb_cutoff = w_bb_cutoff, fleetDynamics=TRUE, selectivity_params = selectivity_params, catchability = df_target_NoCompetition, target = df_target_NoCompetition)
#  
# sim_trial <- project(params_trial, effort = 0, dt = dt, fleetDynamics = TRUE, management = TRUE, multiFleet = FALSE, price = price_forward, cost = cost_forward, diet_steps = 0, ke = ke, initial_effort = initial_effort_scenario, scaling_price = scaling_price, Blevel_management = Blevel_management, initial_n = initial_n_scenario, initial_n_pp = initial_n_pp_scenario , initial_n_bb = initial_n_bb_scenario)
# 
# 
# plotFleet(sim_trial)
# sim_trial@effortOut
# sim_trial@effortOut_dt


####### should recovery speceis not being caought in any of these scenario?! using recent data does not change the target matrix as it details how much of the whatever catch is split into teh main fleet, but may change the list of main fleet - i.f. deep slope may be togethr with eth upper slope 

######## target unfished 
df_target_unfished<-target
df_target_unfished[]<-0

# params_unfished <- MizerParams(df_param, interaction = theta, kappa = kappa, kappa_ben = kappa_ben, kappa_alg = kappa_alg, w_pp_cutoff = w_pp_cutoff, min_w_bb = min_w_bb, w_bb_cutoff = w_bb_cutoff, fleetDynamics=TRUE, selectivity_params = selectivity_params, catchability = df_target_unfished, target = df_target_unfished)

# params_unfished@selectivity
 
# sim_unfished <- project(params_unfished, effort = 0, dt = dt, fleetDynamics = TRUE, management = TRUE, multiFleet = FALSE, price = price_forward, cost = cost_forward, diet_steps = 0, ke = ke, initial_effort = initial_effort_scenario, scaling_price = scaling_price, Blevel_management = Blevel_management, initial_n = initial_n_scenario, initial_n_pp = initial_n_pp_scenario , initial_n_bb = initial_n_bb_scenario )

# plotFleet(sim_unfished) # effort and profits are calcualted anyway - it's OK fixed below   
# plotBiomass(sim_unfished)$plot + facet_wrap(~Species)

######## no competition
library(matrixStats)
df_target_NoCompetition<-target
trial<-colMaxs(df_target_NoCompetition)
trial<-trial[-which(trial == 0)]
df_target_NoCompetition[df_target_NoCompetition %in% trial]<-1
df_target_NoCompetition[df_target_NoCompetition != 1]<-0

# trial 2 - keep Fmort on each target spp constant, just  moved from all fleet to 1 fleet 
div<-colSums(df_target_NoCompetition*initial_effort_scenario)/colSums(target*initial_effort_scenario)
df_target_NoCompetition<-sweep(df_target_NoCompetition, 2, div, FUN = '/')
df_target_NoCompetition[, "myctophids"]<-0  

# colSums(df_target_NoCompetition*initial_effort_scenario)
# colSums(target*initial_effort_scenario)

######## full competition 
df_target_FullCompetition<-target
df_target_FullCompetition[]<-1
df_target_FullCompetition[, "myctophids"]<-0  
# df_target_FullCompetition[, "trachurus declivis"]<-0
# df_target_FullCompetition[, "nototodarus gouldi"]<-0
# df_target_FullCompetition[, "helicolenus barathri"]<-0
# df_target_FullCompetition[df_target_FullCompetition!=0]<-1 # this would be the best, but results are difficult to interpret....

# trial 2 - as above
div<-colSums(df_target_FullCompetition*initial_effort_scenario)/colSums(target*initial_effort_scenario)
df_target_FullCompetition<-sweep(df_target_FullCompetition, 2, div, FUN = '/')
df_target_FullCompetition[, "myctophids"]<-0  

# colSums(df_target_FullCompetition*initial_effort_scenario)
# colSums(target*initial_effort_scenario)

######## no bycatch (and spp under rebilding strategies) 
# NOTE: 2 fisheries are based on spp under recovery strategies - OR and school shark
df_target_NoBycatch<-target
# what's bycatch? the 2 fleets with lowest proportion of catches should not catch the spp? 

df<-target
for(i in 1:ncol(df)){
  df<-df[order(df[,i]),]
  df[c(1,2),i]<-0
}
df<-df[c(2,1,3,4,5),]
df_target_NoBycatch<-df

# trial 2 - as above
div<-colSums(df_target_NoBycatch*initial_effort_scenario)/colSums(target*initial_effort_scenario)
df_target_NoBycatch<-sweep(df_target_NoBycatch, 2, div, FUN = '/')
df_target_NoBycatch[, "myctophids"]<-0  

# this applied to both trial 1 and 2.... Should this be done? cacth is not kept stable this way...
# df_target_NoBycatch[, "seriolella brama"] <- 0 # rebuilding 
# df_target_NoBycatch[, "rexea solandri"] <- 0 # rebuilding 
# # df_target_NoBycatch[, "hoplostethus atlanticus"] <- 0 # rebuilding or not really? 
# df_target_NoBycatch[, "galeorhinus galeus"] <- 0 # rebuilding

colSums(df_target_NoBycatch*initial_effort_scenario)
colSums(target*initial_effort_scenario)

######## target more target - see options    
# define (main target and?) most valuable spp and increase fishing on these by the fleets that already catch them - by 50% - working, set to 1 - not working 
# yes I have checked prices according to data and they match with sharks being the higehst value spp. 
valuable<-sort(-df_price_new[nrow(df_price_new),])
valuable<-names(valuable)[1:6]

# # option 1 
# df_target_MoreTarget<-as.data.frame(target) %>% 
#   mutate(fleet = rownames(target)) %>% 
#   gather(key = "species", value = "interaction", - fleet) %>% 
#   mutate(interaction = ifelse(species %in% valuable & interaction > 0, interaction*2, interaction))
# df_target_MoreTarget<-acast(df_target_MoreTarget, fleet ~ species) 

# option 2 - increase Fmort of valuable by 50% of current Fmort adn spread taht  increase across fleets proportionally
df_target_MoreTarget<-target
a<-colSums(target[,valuable]*initial_effort_scenario) 
a<-a + (a*0.5) # plus 50% ? 
div<-colSums(df_target_MoreTarget[,valuable]*initial_effort_scenario)/a
df_target_MoreTarget[,valuable]<-sweep(df_target_MoreTarget[,valuable], 2, div, FUN = '/')

colSums(df_target_MoreTarget*initial_effort_scenario)
colSums(target*initial_effort_scenario)

######## target more underquota   
# define under quota spp and increase fishing on these. https://www.afma.gov.au/sites/default/files/semac_tac_recommendations_2019-20.pdf
# undercaught TAC is a performance indicator of the fishery - can be added to the socio-economic ones? 
under<-c("macruronus novaezelandiae","nemadactylus macropterus","zeus faber","pristiophorus cirratus") # Jackass morwong is a bit funny as it's declining and there are no data for assessment. redfish?! recovery or undercaught? shawshrk is low values, not overfished 

# # option 1 
# df_target_MoreUnderQuota<-as.data.frame(target) %>% 
#   mutate(fleet = rownames(target)) %>% 
#   gather(key = "species", value = "interaction", - fleet) %>% 
#   mutate(interaction = ifelse(species %in% under & interaction > 0, interaction*2, interaction))
# df_target_MoreUnderQuota<-acast(df_target_MoreUnderQuota, fleet ~ species) 

# option 2 - increase Fmort of valuable by 50% of current Fmort adn spread taht  increase across fleets proportionally
df_target_MoreUnderQuota<-target
a<-colSums(target[,under]*initial_effort_scenario) 
a<-a + (a*0.5) # plus 50% ? 
div<-colSums(df_target_MoreUnderQuota[,under]*initial_effort_scenario)/a
df_target_MoreUnderQuota[,under]<-sweep(df_target_MoreUnderQuota[,under], 2, div, FUN = '/')

colSums(df_target_MoreUnderQuota*initial_effort_scenario)
colSums(target*initial_effort_scenario)

####### runs 
target_scenario = list(unfished = df_target_unfished, noCompetition = df_target_NoCompetition, fullCompetition = df_target_FullCompetition, statusQuo = target, noBycatch = df_target_NoBycatch, MoreTarget = df_target_MoreTarget, MoreUnderQuota = df_target_MoreUnderQuota) # best = df_target_best)

params_scenario<-list()
sim_scenario<-list()

for(i in 1:length(target_scenario)){
  
  # i = 4
  params_scenario[[i]] <- MizerParams(df_param2,
                            interaction = theta, 
                            kappa = kappa,
                            kappa_ben = kappa_ben, 
                            kappa_alg = kappa_alg, 
                            w_pp_cutoff = w_pp_cutoff,
                            min_w_bb = min_w_bb, 
                            w_bb_cutoff = w_bb_cutoff, 
                            fleetDynamics = TRUE, 
                            selectivity_params = selectivity_params,
                            catchability = target_scenario[[i]],
                            target = target_scenario[[i]])

  sim_scenario[[i]] <- project(params_scenario[[i]], 
                      effort = 0, 
                      dt = dt, 
                      fleetDynamics = TRUE, 
                      management = TRUE, 
                      multiFleet = FALSE,
                      price = price_forward, 
                      cost = cost_forward, 
                      diet_steps = 0, 
                      ke = ke,  
                      initial_effort = initial_effort_scenario,
                      scaling_price = scaling_price,
                      Blevel_management = Blevel_management,
                      initial_n = initial_n_scenario,
                      initial_n_pp = initial_n_pp_scenario, 
                      initial_n_bb = initial_n_bb_scenario)
  
  names(sim_scenario)[i]<-names(target_scenario)[i]
  
}

# check one by one

# plotFleet(sim_scenario$unfished)
plotFleet(sim_scenario$noCompetition) # declines in effort and yield despite increases in abundance - why? are declines driven by profits instead of management? when decreases are weigthed by contribution to cacthes they are multiplied by 1 instead of e.g. 0.01 and thus are bigger... (i.e. if a spp contributes a little than the decrease is small, if it contributes a lot - Q=1 - then decreases are bigger). this is the problem with SH, which is forced to steeply decrease because platy has a Q of 1 and is below 20. when platy recovers, changes in effort are less steep.
plotFleet(sim_scenario$fullCompetition) # collapses
plotFleet(sim_scenario$statusQuo) # some recoveries and increases
plotFleet(sim_scenario$noBycatch) # recoveries and increases in trends
plotFleet(sim_scenario$MoreTarget) # collapses
plotFleet(sim_scenario$MoreUnderQuota) # collapses

# why collapses? because more than 4 spp are below 20! fleet collapses mean spp recoveries....
a<-sim_scenario$noCompetition
# plotFleet(a)
# plotBiomass(a)$plot + facet_wrap(~Species)
# managemtn
pr <- a@BioOut[[24]] %>%
  filter(bioLim == "bio20check", fleet == "SET-SH")
unique(pr$species)

a@effortOut
a@profit

# catchComp(sim_FD = sim_scenario$statusQuo, df_log_spp)
trial<-a@yield
trial<-rowSums(aperm(trial,c(1,2,4,3)),dims=3) # sum over size
trial<-as.data.frame.table(trial, responseName = "yield")
colnames(trial)<-c("year", "species","fleet", "yield")
trial<-trial%>%
 left_join(df_param[,c(1,2)])

ggplot(trial,aes(x=year, y = yield, fill=species)) +
  geom_bar(position = "stack", stat = "identity") +
  theme_bw() +
  facet_wrap(~fleet, scale = "free")

```

#-----------------------------------------
# scenarios management *skyp*  
#----------------------------------------------

```{r}
# explore managemtn options - open access, HRC, save the small and save the big.

# params_OA <- MizerParams(df_param,
#                           interaction = theta, 
#                           kappa = kappa,
#                           kappa_ben = kappa_ben, 
#                           kappa_alg = kappa_alg, 
#                           w_pp_cutoff = w_pp_cutoff,# should be 'new' here but may not matter
#                           min_w_bb = min_w_bb, 
#                           w_bb_cutoff = w_bb_cutoff, 
#                           fleetDynamics = TRUE, 
#                           selectivity_params = selectivity_params,
#                           catchability = catchability,
#                           target = target)
# 
# sim_OA<- project(params_OA, 
#                       effort = 0, 
#                       dt = 0.5, 
#                       fleetDynamics = TRUE, 
#                       management = FALSE, # problem here.... 
#                       price = price_forward, 
#                       cost = cost_forward, 
#                       diet_steps = 0, 
#                       ke = ke, # should be calibrated here  
#                       initial_n = initial_n_scenario,
#                       initial_n_pp = initial_n_pp_scenario, 
#                       initial_n_bb = initial_n_bb_scenario, 
#                       initial_effort = initial_effort_scenario, 
#                       scaling_price = scaling_price, # should be calibrated values here 
#                       Blevel_management = Blevel_management)
# 
# 
# # plotFleet(sim_OA)
# # plot_CN(sim_OA)
# 
# # explore management
# 
# # HCR to target spp only
# 
# # NOTE: catchability is used to determine which spp each fleet catches (getFmortGear()); target is used to select which spp are under management (in management component)).
# 
# df_target_management<-df_target_bmsy
# df_target_management[, c("centroberyx affinis","helicolenus barathri","myctophids","nototodarus gouldi","pristiophorus cirratus","squalus spp.","trachurus declivis","zeus faber")]<-0
# 
# params_HCR <- MizerParams(df_param,
#                             interaction = theta,
#                             kappa = kappa3,
#                             kappa_ben = kappa_ben,
#                             kappa_alg = kappa_alg,
#                             w_pp_cutoff = w_pp_cutoff,
#                             min_w_bb = min_w_bb,
#                             w_bb_cutoff = w_bb_cutoff,
#                             fleetDynamics = TRUE,
#                             selectivity_params = df_selParam_new,
#                             catchability = df_target_bmsy,
#                             target = df_target_management)
# 
# sim_HCR<- project(params_HCR,
#                       t_max = t_max,
#                       effort = 0,
#                       dt = 0.5,
#                       fleetDynamics = TRUE,
#                       management = TRUE,
#                       price = df_price_new,
#                       cost = df_cost_mean2,
#                       diet_steps = 0,
#                       ke = ke,
#                       initial_n = initial_n,
#                       initial_n_pp = initial_n_pp,
#                       initial_n_bb = initial_n_bb,
#                       initial_effort = initial_effort,
#                       scaling_price = scaling_price,
#                       Blevel_management = Blevel_management)
# 
# plotFleet(sim_FD)
# plotFleet(sim_HCR)
# plot_CN(sim_FD)
```

#-----------------------------------------
# size limits *move to Multifleet_example* 
#----------------------------------------------

```{r}

names(sim_scenario)

# selectivity - save small individuals
params_saveSmall<-sim_scenario$statusQuo@params # params where target and catchability is as per status quo 
dim(params_saveSmall@selectivity)
params_saveSmall@selectivity[1,5,] # fleet, species, size 
params_saveSmall@selectivity[,,1:71]<-0 # this needs to be species-specific!

saveSmall <- project(params_saveSmall, 
                      effort = 0, 
                      dt = dt, 
                      fleetDynamics = TRUE, 
                      management = TRUE, 
                      multiFleet = FALSE,
                      price = price_forward, # running with price and cost data between 2006 and 2017 as per above 
                      cost = cost_forward, 
                      diet_steps = 0, 
                      ke = ke,  
                      initial_n = initial_n_scenario, # running with values from 2006 as per above
                      initial_n_pp = initial_n_pp_scenario, 
                      initial_n_bb = initial_n_bb_scenario, 
                      initial_effort = initial_effort_scenario, 
                      scaling_price = scaling_price, 
                      Blevel_management = Blevel_management)

plot_CN(saveSmall)
plotFleet(saveSmall)
plotFleet(sim_scenario$statusQuo)

# selectivity - save big individuals
params_saveBig<-sim_scenario$statusQuo@params
params_saveBig@selectivity[,,90:100]<-0 

saveBig <- project(params_saveBig, 
                      effort = 0, 
                      dt = 0.5, 
                      fleetDynamics = TRUE, 
                      management = TRUE, 
                      price = price_forward, # running with price and cost data between 2006 and 2017 as per above 
                      cost = cost_forward, 
                      diet_steps = 0, 
                      ke = ke,  
                      initial_n = initial_n_scenario, # running with values from 2006 as per above
                      initial_n_pp = initial_n_pp_scenario, 
                      initial_n_bb = initial_n_bb_scenario, 
                      initial_effort = initial_effort_scenario, 
                      scaling_price = scaling_price, 
                      Blevel_management = Blevel_management)

plot_CN(saveBig)
plotFleet(saveBig)
plotFleet(sim_scenario$statusQuo)

sim_saveBig@effortOut[t_max,]

BioOut<-do.call("rbind",saveBig@BioOut)
BioOut40<-BioOut[BioOut$time == t_max & BioOut$bioLim %in% c("bio40check"),]
BioOut20<-BioOut[BioOut$time == t_max & BioOut$bioLim %in% c("bio20check"),]

```

# TO DO 

See ecovariability paper 
objectives (i.e. expressed in managemtn rules): 
1. blim
2. yiled lim
3. profit positive for all fleets

scenarios: 
1. fleets driven by current effort and managemtn is off
2. MEY - fleets driven by profits and Blim on
3. minimise bioeconomic risk of vulnerability - all management rules applied  

indicators:  
1. net present value (i.e. profits - economic)
2. meeting objectives (Blim, yiled lim and profit > 0 - ecoviablility only for scenario 3)
3. richness, trophic index, simpson (ecological)

my model: 
objectives: 
1. blim
2. maximise profits (not care about fleet profitability)

scenario: 
1. full competition 
2. no competition ... 

indicators: 
1. yield (in my case not an objective but an indicators), effort, profit
2. meeting objectives (n spp above Blim, could aslo do n fleet active but not an objective)
3. biomass (better not as it's in management)
4. slope and trophic level  


#-----------------------------------------
# plots of comparison 
#----------------------------------------------


```{r}

### delete unfished as not used
sim_scenario$unfished<-NULL
# some fixes: 
# sim_scenario[["unfished"]]@effortOut[]<-0 # beaause initial_effort was still 0.1 though catches are 0 due to df_target
# sim_scenario[["unfished"]]@profit[]<-0 # because fixed costs were still there 
# sim_scenario[["unfished"]]@revenue[]<-0 # becasue of the above 

# Calculate indicators at last run of scenarios - whole fishery level 
indi<-indicators(sim_scenario)
df_plot = indi$df_plot

# order of scenarios
a = c("statusQuo","noCompetition","fullCompetition","noBycatch","MoreTarget","MoreUnderQuota")
b = c("Status Quo","No Competition","Full Competition", "Less Bycatch","More Valuable","More Under-Quota")
# col_values<-c("#084594", "#2171b5", "#eff3ff", "#c6dbef", "#9ecae1", "#6baed6", "#4292c6") # https://colorbrewer2.org/#type=sequential&scheme=Blues&n=7
col_values<-c("#08589e", "#2b8cbe", "#4eb3d3", "#7bccc4", "#a8ddb5", "#ccebc5", "#f0f9e8") # https://colorbrewer2.org/#type=sequential&scheme=Blues&n=7

# plot fishing effort by fleet
plot_effort = plotFleetEffort(a,b, sim_scenario, sim_FD_bmsy, col_values[1:5])$plot_effort
plot_effort

# plot interaction matrix
plot_matrix = plotFleetMatrix(a,b,target_scenario, col_values[2])$plot_matrix

# plot indicators - fisry level 
plot_bar_reduced = plotIndicators(a,b,df_plot, col_values[c(2,4)])$plot_bar_reduced # this one 
plot_bar_reduced

# all plots 
library(patchwork)
setwd("/Users/nov017/Dropbox/Mizer-fleet_extension/plot/FD")
tiff("Fig4_May2020.tiff", height=13, width=16, units ='in', res=300)
# plot_matrix / plot_bar + plot_layout (nrow = 2, heights = c(2,2))
plot_matrix / plot_effort / plot_bar_reduced + plot_layout (nrow = 3, heights = c(2.2,1.4,1.4))
dev.off()


```

# TO DO BETH

FIRST - OK
decreases in effort - per broken stick 
A most limiting spp set effort reduction - reduce effort according to the species that is below msy - reduce by the amount of the depletion (e.g. by 10% is the spp is depleted by 10%)
B mean (which mean? up to you) of any reduction: 
effort scaler = 1/3 (a + b + c) - TRIED 
effort scaler = cube root of (a * b * c) 
effort scaler = (a*Ba + b*Bb + c*Bc)/(Ba + Bb + Bc) = weighted sum of contributing species
if B is on, then you don't need the 20% rule 

SECOND OK  
burning period or stabilzations at the FD level - don't do it as you are missing the dynamics and taking/exploring the system at another level.  

THIRD
fleet behaviour rule before the managetmn if thinkgs are still not working as expected...
E ~ profit -> if profit < lower bound, reduce effort by a certain % and vice versa. figure out the bound looking at CPUE and effort. 

FIFTH
plot of relative biomass vs bmsy and Blim for each stock and scenario
time series of effort levels - as for plotFleet()

SIXTH
in the time variant but relevant in genetal, effort might not dcrease even if profits do becasue changes in costs produce a very low change in effort e.g. 0.00000001 that is too low to be reflected in profits. Need to change the price something? need to think about this!!! 

SEVENTH - OK
do not consider MTL as it has many problems.... change with others

#-----------------------------------------
# additional plots 
#----------------------------------------------

```{r}

# function to plot model runs - species with biomass limits 
plot_limits<-function(temp_sim){
  
  temp_sim = sim_scenario_list[[1]] # to fix....
    
  BioData<-plotBiomass(temp_sim)$BioData
  BioLim<-temp_sim@BioLimits[[dim(temp_sim@effortOut)[2]]]
  dim(temp_sim@BioLimits)
  colnames(BioLim)<-c("Species", "bioLevel","bio20","bio40","bio48")

  BioLim <-BioLim %>% 
    mutate(bio20 = ifelse(Species %in% c("trachurus declivis","nototodarus gouldi","helicolenus barathri"), NA, bio20),
           bio40 = ifelse(Species %in% c("trachurus declivis","nototodarus gouldi","helicolenus barathri"), NA, bio40),
           bio48 = ifelse(Species %in% c("trachurus declivis","nototodarus gouldi","helicolenus barathri"), NA, bio48))

  names(spNames) <- unique(BioData$Species)

  x_label <- "Year"
  y_label <- "Biomass [g]"
  p <- ggplot(BioData, aes(x = time, y = value)) +
    scale_y_continuous(trans = "log10", # breaks = log_breaks(n = 3)
                           labels = prettyNum, name = y_label) +
    scale_x_continuous(name = x_label) +
    geom_line() + 
    theme_bw()+
    geom_hline(data = BioLim, aes(yintercept = bio20), linetype = "dotdash", color = "red")+
    geom_hline(data = BioLim, aes(yintercept = bio40), linetype = "dashed", color = "green")+
    geom_hline(data = BioLim, aes(yintercept = bio48), linetype = "dotted", color = "blue")+
    theme(text = element_text(size=18),
          axis.title.y = element_text(vjust=0.4, size = 16),
          axis.title.x = element_text(vjust=0.3, size = 16),
          axis.text.x = element_text(angle=90, hjust=0.5),
          panel.grid.major = element_blank(), 
          strip.background =element_rect(fill="white"),
          legend.position = "none")+
    facet_wrap(~Species, 
               labeller = labeller(Species = spNames))
  
  return(p)
}

# function to plot model runs - fleets effort, profits, yield etc.  

plot_fleet<-function(temp_sim){
  # plot_fleet<-plotFleet(temp) # OR
  
  eData<-plotEffort_CN(temp_sim)$eData
  colnames(eData)<-c("time","fleet","Effort [m]")
  yData<-plotYield_CN(temp_sim)$yData
  colnames(yData)<-c("time","fleet","Yield [g]")
  prData<-plotProfit_CN(temp_sim)$prData
  colnames(prData)<-c("time","fleet","Profit [$]")

  fleetData<-merge(eData, yData, all = TRUE)
  fleetData<-merge(fleetData, prData, all = TRUE)
  fleetData<-fleetData %>%
    gather(key, value, -time, -fleet)

  x_label <- "Year"
  p <- ggplot(fleetData, aes(x = time, y = value)) +
    scale_x_continuous(name = x_label) +
    geom_line() +
    theme_bw()+
    theme(text = element_text(size=18),
          axis.title.y = element_blank(), 
          axis.title.x = element_text(vjust=0.3, size = 16),
          panel.grid.major = element_blank(),
          strip.background =element_rect(fill="white"),
          legend.position = "none")+
    facet_grid(key~fleet, scale = "free")
  
  return(p)
}

# run function over each scenario 

plot_SI_sim_scenario<-list()

for(i in 1:length(sim_scenario_list)){
  
  i = 6
  a<-plot_limits(sim_scenario_list[[i]])
  b<-plot_fleet(sim_scenario_list[[i]])
  # library(patchwork)
  plot_SI_sim_scenario [[i]]<- a / b + plot_layout (nrow = 2, heights = c(1.5,1))
  
  names(plot_SI_sim_scenario)[i]<-names(sim_scenario_list)[i]
  
}

# not working! only manually.... 

for(i in 1:length(plot_SI_sim_scenario)){
 
  i = 6
  setwd("/Users/nov017/Dropbox/Mizer-fleet_extension/plot/FD")
  tiff(paste("FigS6_",names(plot_SI_sim_scenario)[i],".tiff", sep = "" ), height=10, width=10, units ='in', res=300)
  plot_SI_sim_scenario[[i]]
  dev.off()
  
}

```

