---
title: "SEAmodel_run_FD"
author: "Camilla Novaglio"
date: "15/11/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# key folders: 

# summary of communities: 

#-----------------------------------------
# Load code and data produced in SEmodel_run  
#-----------------------------------------

```{r codes}

rm(list=ls())

# 3 options according to the SEAmodel_run.Rmd
# load("/Users/nov017/Dropbox/Mizer-fleet/R/model/tempData.RData") # now SEAmodel_opn1.RData.
# load("/Users/nov017/Dropbox/Mizer-fleet/R/model/tempData_Oct.RData") # now SEAmodel_opn2.RData
# load("/Users/nov017/Dropbox/Mizer-fleet/R/model/SEAmodel_opn3.RData") # before tempData_Nov.RData

# now changed folder 
load("/Users/nov017/Dropbox/Mizer-fleet_extension/data/SEAmodel_opn3.RData") 

library(tidyverse)
library(devtools)
library(plyr) 
library(Rcpp) # this will allow you to run the inner_project_loop 
library(reshape2)
library(inline)
library(ggplot2)
library(vegan)
# install.packages("shiny")
library(mizer) # if inner_loop error, you need to upload mizer
library(shiny)

setwd("/Users/nov017/Dropbox/Mizer-fleet/R")
source("data.R") 
source("help.R") 
source("MizerParams-class.R") 
source("MizerSim-class.R")
source("plots.R")
source("project_methods.R")
source("project.R")
source("RcppExports.R") 
source("selectivity_funcs.R")
source("summary_methods.R")
source("wrapper_functions.R")
source("DataFunction.R") 

```

#-----------------------------------------
# (re)calculate df_target
#----------------------------------------------

```{r}

# See SEA_FleetParam.Rmd option 3 (calcualte Q from catches) line 634 for ref 

# filter speceies and metiers before calculating target matrix 
df_main_metier<-c("GHAT - Southern Shark Gillnet","South East Trawl Fishery - Danish Seine","South East Trawl Fishery - Otter trawl shelf","South East Trawl Fishery - Otter trawl upperSlope", "South East Trawl Fishery - Otter trawl deepSlope") 

catch <- df_log_spp %>%
  filter(metier %in% df_main_metier) %>% 
  filter(SPC_NAME %in% df_param$species) %>%  
  group_by(SPC_NAME, metier) %>%
  dplyr::summarize(
    catch_kg = sum(TOT_CATCH_KG, na.rm=TRUE)
  ) %>% 
  `colnames<-`(c("species","metier", "catch_kg"))

# add spp missing from catch data
other_spp<-expand.grid(unique(df_param$species), unique(catch$metier))
colnames(other_spp)<-c("species","metier")
catch<-merge(catch, other_spp, all = TRUE)
catch[is.na(catch$catch_kg),"catch_kg"]<-0

# option 2 - consider speceis (instead of fleets)
df_qcatch<-split(catch, catch$species)

# calcualte proportions by speceis
for(i in 1:length(df_qcatch)){
  mi = sum(df_qcatch[[i]]$catch_kg)
  df_qcatch[[i]]$catch_prop<-(df_qcatch[[i]]$catch_kg/mi)
}

df_qcatch<-data.frame(do.call("rbind",df_qcatch))
rownames(df_qcatch)<-NULL
df_qcatch<-df_qcatch[,-which(colnames(df_qcatch) =="catch_kg")]
colnames(df_qcatch)<-c("species","subfleet","target") 
df_qcatch[which(df_qcatch$species %in% c("myctophids")),"target"]<-0 

# change fleet names
df_qcatch<-df_qcatch %>% 
  mutate(subfleet = case_when(subfleet == "GHAT - Southern Shark Gillnet" ~ "SSG",
                              subfleet == "South East Trawl Fishery - Danish Seine" ~ "SED",
                              subfleet == "South East Trawl Fishery - Otter trawl deepSlope" ~ "SET-DS",
                              subfleet == "South East Trawl Fishery - Otter trawl shelf" ~ "SET-SH",
                              subfleet == "South East Trawl Fishery - Otter trawl upperSlope" ~ "SET-US"))

# target and Q don't have the spp order right, but are fixed in Mizerparams-class
df_target = acast(df_qcatch, formula = subfleet ~ species, value.var = "target")
df_target<-df_target[,colnames(relative_effort)]

# this is what will be used in all function to sort fleets 
fleet = rownames(df_target)

# plot matrix
target_plot<-df_qcatch %>%
  right_join(df_param[c(1,2)])

p_target <- ggplot(target_plot, aes(spCommon,subfleet)) +
  geom_tile(aes(fill = target)) +
  scale_fill_gradient(low = "white",high = "blue")+
  theme_bw()+
  theme(text = element_text(size=18),
        axis.text.x = element_text(angle=90, hjust=0.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank())

# adjust df_target to include catchability in df_param ...  
# df_target<-as.data.frame(df_target) %>%
#   mutate(fleet = rownames(df_target)) %>% 
#   gather(species, q, -fleet) %>% 
#   left_join(df_param[,c("species", "catchability")]) %>% 
#   mutate(q = q*catchability) %>% 
#   select(-catchability) %>% 
#   spread(species, q)
# rownames(df_target)<-df_target$fleet
# df_target<-df_target %>% select(-fleet)
# df_target<-as.matrix(df_target)

```

# TO DO  
need to change the description of the target matrix in the paper? No difference
- old option: when considering the proportion of catch by fleet: the total catch of each fleet sums to 1, but the total catch of each spp could be higher than 1; i.e. yield > biomass (yield = biomass X target X effort).
- when considering the proportion of catch by speceis: the total catch of each speceis sums to 1, but the total catch for each fleet can be higher than 1 (e.g. trawlin cacthes 0.9 of many spp).  
- BIG EYE is caught here but not in the model above with Fmort - to check and add Fmort based on catches for this spp. 



#-----------------------------------------
# adjust df_selParam_new, df_price_new, df_cost2
#----------------------------------------------

```{r}

# keep only spp and fleets specified above
df_selParam_new<-df_selParam %>% 
  filter(species %in% df_param$species, 
         subfleet %in% df_main_metier) %>% 
  mutate(subfleet = case_when(subfleet == "GHAT - Southern Shark Gillnet" ~ "SSG",
                              subfleet == "South East Trawl Fishery - Danish Seine" ~ "SED",
                              subfleet == "South East Trawl Fishery - Otter trawl deepSlope" ~ "SET-DS",
                              subfleet == "South East Trawl Fishery - Otter trawl shelf" ~ "SET-SH",
                              subfleet == "South East Trawl Fishery - Otter trawl upperSlope" ~ "SET-US"))

df_price_new<-df_price %>% 
  filter(species %in% df_param$species)

# add values for 2017
addPrice2017<-df_price_new %>% 
  filter(year == "2016") %>% 
  mutate(year = "2017")
df_price_new<-rbind(df_price_new, addPrice2017)

# matrix of prices
df_price_new = spread(df_price_new, species, price)
rownames(df_price_new)<-df_price_new$year
df_price_new<-df_price_new[,-1]
df_price_new<-as.matrix(df_price_new)
df_price_new<-df_price_new[, df_param$species] # order spp

# cost - can have differnt units 
# df_cost = df_cost_g $ opn-1 g-1
# df_cost2 = df_cost_opn $ opn-1

# divide fixed and variable costs - variable costs vary with the amount of fishing effort or catch, and fixed costs do not vary with effort (Pascoe 2014)

# After chat with Beth and Ingrid - use cost/g - still need to figure out units in eqn... 

df_cost2<-df_cost_opn %>% 
  filter(subfleet %in% df_main_metier) %>% 
  mutate(cost_type = ifelse(param_type %in% c("Crew","Fuel","Packaging","Freight"), "fixed", "variable")) %>% 
  group_by(subfleet, year, cost_type) %>%  
  dplyr::summarise(cost = sum(param_value, na.rm=TRUE)) %>% 
  mutate(subfleet = case_when(subfleet == "GHAT - Southern Shark Gillnet" ~ "SSG",
                              subfleet == "South East Trawl Fishery - Danish Seine" ~ "SED",
                              subfleet == "South East Trawl Fishery - Otter trawl deepSlope" ~ "SET-DS",
                              subfleet == "South East Trawl Fishery - Otter trawl shelf" ~ "SET-SH",
                              subfleet == "South East Trawl Fishery - Otter trawl upperSlope" ~ "SET-US"))

# cost need to have the same years as price - temporary values here 
addCost2015<-df_cost2 %>% 
  filter(year == "2014") %>% 
  mutate(year = "2015")
addCost2016<-addCost2015 %>% 
  mutate(year = "2016")
addCost2017<-addCost2015 %>% 
  mutate(year = "2017")
df_cost2<-rbind(df_cost2,addCost2015,addCost2016, addCost2017)

# matrix of costs
df_cost2<-acast(df_cost2, formula = year ~ subfleet ~ cost_type, value.var = "cost") 
df_cost2<-df_cost2[,rownames(df_target),] # order cost by fleet

# OPTION 1 use costs in g or use costs in g rescaled as per Beth's data - NO CHANGE from above
# Beth's adjustment on costs - see email 'price' and file 'costs_from_SESSF_2005'

ref<- df_cost2[,3,1] # trawlers on the shelf
df_cost2[,1,1]<-ref*1.5 # Danish seiners - see agenda, could be *0.6 or *1.5?
df_cost2[,2,1]<-ref*0.67 # deep slope
df_cost2[,4,1]<-ref*0.67 # upper slope - these is the fishery using the biggers adn more expensive boats, so if you are using the costs per operation unit, this should be highest
df_cost2[,5,1]<-ref*0.94 # gillnet

ref<- df_cost2[,3,2] # trawlers on the shelf
df_cost2[,1,2]<-ref*1.5 # Danish seiners
df_cost2[,2,2]<-ref*0.67 # deep slope
df_cost2[,4,2]<-ref*0.67 # upper slope
df_cost2[,5,2]<-ref*0.94 # gillnet

```

# Problem from previous version (IMBeR version): 
1. not possible to reproduce observed trends in catches and effort etc. after calibrating ke and scaling price parameters with the FD running - and this is because the calibration forced the model to reach equilibrium, which due to model structure and managemtn constrains is when MEY is reached and effort is stabilised. loosing dynamics. So instead, run the time variant version of the FD model without FD calibraion and tune parameters for a better fit. 
2. no costs difference between fleets results in fitting problems. Use costs in g (cost of fishing 1 g of fish and different between fleets as bsed on catches) instead of coasts per operation (same for all trawling as based on data at teh fishery level?). Also, could use costs in g calculated for trawlers of the shelf and rescale that using scaling factors from beth (Atlantis)
3. check for bugs in managemtn as at present fishing steeply declines if only one specis is declining despite the  

# TO DO 
there are data on profits that can be used for calibration/validation - see xlsx file and ASK INGRID on how to use these data


#-----------------------------------------
# Set fixed parameters
#----------------------------------------------

```{r}

kappa = kappa # intercpet of PP
kappa_ben = kappa_ben # intercpet of BB benthic spectrum
kappa_alg = kappa_alg # intercpet for algae spectrum
lambda = 2.33 # slope of spectrum - def
lambda_ben = 2.33 # slope of spectrum - def
w_pp_cutoff = w_pp_cutoff 
min_w_bb = min_w_bb
w_bb_cutoff = w_bb_cutoff  
n = 2/3 # Exponent for max. food intake - def
q = 0.8 # Exponent for volumetric search rate - def
dt = 0.25
no_w = 100 # def

```

#-----------------------------------------
# Calculate biomass reference levels  
#----------------------------------------------

```{R}

# Calculate biomass reference levels (Bref, Bmsy, Bhist) 
Blevel<-getBlevel(sim_calibrated_unfished,matrix_effort_nofishing,constant_effort,sim_calibrated,df_param,sim_fitted)
bioUnfished = Blevel$bioUnfished 
msy = Blevel$msy
p = Blevel$p
Bhist = Blevel$Bhist

# add bioUnfished, Bmsy and Bhist, B0 as per SA to df_param 
df_param<-df_param %>% 
  left_join(select(msy, c(species, Bmsy))) %>% 
  left_join(select(Bhist, c(species, Bhist))) %>% 
  left_join(bioUnfished %>% dplyr::rename(Bref = bioUnfished)) %>% 
  mutate(B0_SA = (getBiomass(sim_calibrated)[200,])*100/df_param$changesSSB)

# plot values
bio<-df_param %>%
  select(species, Bref,Bmsy,Bhist,B0_SA) %>%
  mutate(bioMod = getBiomass(sim_calibrated)[200,])

bio_plot<-bio %>% gather(variable, value, -species)

p<-ggplot(bio_plot, aes(x = variable, y = value))+
    geom_point()+
    facet_wrap(~species, scale ="free_y")+
    theme(axis.text.x = element_text(size=10, angle = 90, hjust=0.5))

# check reference levels. using Bmsy and Bhist, fishing is more likely to happen
# bio$fishing<-ifelse(bio$bioMod<bio$Bmsy*0.5, "no fishing", "")

```

# TO DO
1. need to transfor all of this from input (effort) to output (catch) control 
2. how do we calculate Bmey instead of 1.2*Bmsy (https://www.youtube.com/watch?v=7DNhqtYf47E)? By running the model increasing costs instead of effort?
3. add compliance term in effort equation? 


#-----------------------------------------
# Calculate scaling costs and price  
#---------------------------------------------- 

```{r}

# scaling cost area - to get units right
# from costs in $ g-1 opn-1 to costs in $ g-1 m-3
# m3 fished in a tralwing operation:
scaling_cost_area = 14000*10*20 # SESSFdataCleaning (trawling+gillnet opn) m trawled*net opening: 20m *10m
scaling_cost_area = scaling_cost_area*5000 # interpretation: soak time for a net (Beth)
df_cost3<-df_cost2
df_cost3[]<-df_cost3/scaling_cost_area 

# scaling costs 
scaling_costs<-1 # interpretation: subsidies? 
scaling_costs<-c(0.000001,1,1,1,1) # making SED very cheap to run -> positive profits -> increase in effort if no spp < 40%
df_cost3[,1,] = df_cost3[,1,]*scaling_costs[1] 
df_cost3[,2,] = df_cost3[,2,]*scaling_costs[2]
df_cost3[,3,] = df_cost3[,3,]*scaling_costs[3]
df_cost3[,4,] = df_cost3[,4,]*scaling_costs[4]
df_cost3[,5,] = df_cost3[,5,]*scaling_costs[5]

# scaling price
scaling_price<-1
df_price_new[]<-df_price_new*scaling_price

```

#-----------------------------------------
# Calcualte fleet param (ke_fleet, initial effort, scaling effort) 
#----------------------------------------------

```{r}

# ke_fleet is effective only if no spp below 40 or if decreases in profit would result in higher decreases than those due to management. The lower ke, the lower the rate of change
ke_fleet = data.frame(fleet= rownames(df_target), ke = rep(1, 5)) 
ke_fleet = data.frame(fleet= rownames(df_target), ke = c(500000,70000,250000,500000,10))

# initial effort (from data)
# see campareTrends for more info on how effort data is treated and plotted.
# can sum(initial_effort) be >1 ? what is the meaning? 
trial<-datValidationEffort %>% 
  ungroup() %>% 
  mutate(opn = (opn*scaling_cost_area)/areaEco) %>% # from opn to m3 trawled in m3
  filter(YEAR == 2006)
trial<-trial[c(3,4,5,6,1),] # reorder fleets
initial_effort = trial$opn

# scaling effort
scaling_effort<-rep(1,5)
initial_effort = initial_effort*scaling_effort

```

#-----------------------------------------
# Tune Q *opn2 - obsolete*
#----------------------------------------------

```{r}

# initial_effort*df_target needs to be on the scale of relative_effort 
colSums(df_target*initial_effort) # this is based on catch and effort data
relative_effort[212,] # this is Fmort from SA (or catches) 

# df_target is not real Q as the one incorporated in Fmort, it sums to 1 and is a proportion of how much each fleet cacthes the whole papolation available.
df_target_bmsy <- df_target

# for squid and tracurus, df_target assumes these spp are fished by the fleets indicated here. but they are not and their catchability is usiually quite low - here represented as food 
df_target_bmsy[, "nototodarus gouldi"]<- df_target_bmsy[, "nototodarus gouldi"]/25 
df_target_bmsy[, "trachurus declivis"]<- df_target_bmsy[, "trachurus declivis"]/40

# OPTION 1 fix upper slope 
df_target_bmsy[4, "seriolella punctata"]<- df_target_bmsy[4, "seriolella punctata"]/2 

# OPTION 2 fix shelf - move target from shelf to sed 
df_target_bmsy[3, "centroberyx affinis"]<- df_target_bmsy[3, "centroberyx affinis"]/2
df_target_bmsy[3, "nemadactylus macropterus"]<- df_target_bmsy[3, "nemadactylus macropterus"]/2
df_target_bmsy[3, "seriolella brama"]<- df_target_bmsy[3, "seriolella brama"]/2 

# OPTION 4 fix sed increase catch by moving some spp from shelf to sed 
df_target_bmsy[1, "centroberyx affinis"]<- df_target_bmsy[1, "centroberyx affinis"]*500
df_target_bmsy[1, "nemadactylus macropterus"]<- df_target_bmsy[1, "nemadactylus macropterus"]*10
df_target_bmsy[1, "seriolella brama"]<- df_target_bmsy[1, "seriolella brama"]*50

# OPTION 5 increase sed effort by removing some declning spp - need to reduce these as much as possible 
df_target_bmsy[1, "helicolenus barathri"]<- 0
df_target_bmsy[1, "seriolella punctata"]<- 0
df_target_bmsy[1, "galeorhinus galeus"]<- 0
df_target_bmsy[1, "squalus spp."]<- 0
df_target_bmsy[1, "centroberyx affinis"]<- 0

# OPTION 6 decrease catches in US
# df_target_bmsy[4, "macruronus novaezelandiae"]<- df_target_bmsy[4, "macruronus novaezelandiae"]/1.5
df_target_bmsy[4, "helicolenus barathri"]<- df_target_bmsy[4, "helicolenus barathri"]/2 # could increase this to 8 as this spp is not an important one? but need to think mode of this 
df_target_bmsy[4, "galeorhinus galeus"]<- 0
df_target_bmsy[4, "centroberyx affinis"]<- df_target_bmsy[4, "centroberyx affinis"]/2

# OPTION 7 - decrease shelf catch 
df_target_bmsy[3,]<-df_target_bmsy[3,]*0.8

# OPTION 8 - decrease blue w 
# df_target_bmsy[1, "seriolella brama"]<- df_target_bmsy[1, "seriolella brama"]*0.1
# df_target_bmsy[3, "seriolella brama"]<- df_target_bmsy[3, "seriolella brama"]*0.1
# df_target_bmsy[4, "seriolella brama"]<- df_target_bmsy[4, "seriolella brama"]*4
# df_target_bmsy[5, "seriolella brama"]<- df_target_bmsy[5, "seriolella brama"]*0.1

# BETH: 
# need to fix blue wharehow (seriorelle b.) -> reduce bycatch from other fisheries
# need to fix flathead -> catch are increasing 
# check increasing abundances - if not realistic you need to change growth parameters and/or recruitment param - see sharks as they all recover to 1995 (modelled) values - though 1995 is a 'depleted' year/abundance 

# 2 problems with flathead: 1) Fmort in 2006 is much lower than for the Fmort model:  
colSums(df_target_bmsy*initial_effort)
relative_effort[212,]

colSums(df_target*initial_effort)
relative_effort[212,]

# I can
# a) increase Q for SED by 8 time. That results in about the same Fmort and fixes the flathead trend. BUT total Q for flathead is Q is 3.7!; trends in whiting is not great as well as trends at teh fleet level in particular for SED
# df_target_bmsy[1,"platycephalus richardsoni"]<-df_target_bmsy[1,"platycephalus richardsoni"]*8
# b) increase effort for e.g. SED (or SET) and decrease Q for all spp but flathed. BUT the effort plots won't look as good and initial effort is not based on data any longer

# 2 predation release from squid, which declines (larvae predation as squid eats fish individuals that are ~12 g not sharks as they enter the community at a much higher weight) 
theta2<-theta
# theta2["nototodarus gouldi",] 
# theta2["nototodarus gouldi","platycephalus richardsoni"]<-3
# I can 
# a) increase predation from other small fish. but this is very slightly effective 
# theta2["sillago flindersi","platycephalus richardsoni"]<-1

# to conclude: the problem is a combination of fishing mortality being low and predation being low so that the population increases. An important problem with both model is that flathead abundance is well underestimated (~ 5000t in model and 20000 t in SA - I remember the problem with flathead in the Fmort model being tat increases in this spp lead to decreases/collapses/increases of squalus).  

```

#-----------------------------------------
# tune Q *opn3 - better*
#----------------------------------------------


```{r}

# initial_effort*df_target = relative_effort as they both determine catches by spp 
colSums(df_target*initial_effort) # based on catch and effort data and used in FD
relative_effort[212,] # Fmort from SA (or catches) and used in previous model 

# rescale df_target*initial_effort using catchability
# calculate catchability
div<-relative_effort[212,]/colSums(df_target*initial_effort)
# what to do with values >1 ? can these be transfered to other param - e.g. initial effort? 
div[div>1]<-1

df_target_bmsy<-df_target
df_target_bmsy<-sweep(df_target_bmsy, 2, div, FUN = '*')
df_target_bmsy[,1]<-0 # mycto
df_target_bmsy[,11]<-df_target_bmsy[,11]*0.8 # seriorela 

colSums(df_target_bmsy*initial_effort)
relative_effort[212,]

# Arrivata qui - need to check the calibration below 

# further calibration - try options above  
# fix upper slope 
df_target_bmsy[4, "seriolella punctata"]<- df_target_bmsy[4, "seriolella punctata"]/2 
# move target from shelf to sed 
df_target_bmsy[3, "centroberyx affinis"]<- df_target_bmsy[3, "centroberyx affinis"]/2
df_target_bmsy[3, "nemadactylus macropterus"]<- df_target_bmsy[3, "nemadactylus macropterus"]/2
df_target_bmsy[3, "seriolella brama"]<- df_target_bmsy[3, "seriolella brama"]/2 
df_target_bmsy[1, "centroberyx affinis"]<- df_target_bmsy[1, "centroberyx affinis"]*500
df_target_bmsy[1, "nemadactylus macropterus"]<- df_target_bmsy[1, "nemadactylus macropterus"]*10
df_target_bmsy[1, "seriolella brama"]<- df_target_bmsy[1, "seriolella brama"]*50

# increase sed effort by removing some declning spp 
df_target_bmsy[1, "helicolenus barathri"]<- 0
df_target_bmsy[1, "seriolella punctata"]<- 0
df_target_bmsy[1, "galeorhinus galeus"]<- 0
df_target_bmsy[1, "squalus spp."]<- 0
df_target_bmsy[1, "centroberyx affinis"]<- 0

# decrease catches in US
df_target_bmsy[4, "helicolenus barathri"]<- df_target_bmsy[4, "helicolenus barathri"]/2 
df_target_bmsy[4, "galeorhinus galeus"]<- 0
df_target_bmsy[4, "centroberyx affinis"]<- df_target_bmsy[4, "centroberyx affinis"]/2

# decrease shelf catch 
df_target_bmsy[3,]<-df_target_bmsy[3,]*0.8

```

#-----------------------------------------
# First model run
#----------------------------------------------

```{r}

# start with community in 2006 (sim_fitted) or community at equilibium (sim_calibrated)
initial_n = sim_fitted@n[212,,]
initial_n_pp = sim_fitted@n_pp[212,]
initial_n_bb = sim_fitted@n_bb[212,]

params_FD <- MizerParams(df_param, interaction = theta2, kappa = kappa, kappa_ben = kappa_ben, kappa_alg = kappa_alg, w_pp_cutoff = w_pp_cutoff, min_w_bb = min_w_bb, w_bb_cutoff = w_bb_cutoff, fleetDynamics = TRUE, selectivity_params = df_selParam_new, catchability = df_target_bmsy, target = df_target_bmsy)

# params_FD@psi
# params_FD@intake_max
# params_FD@search_vol
# params_FD@metab
# params_FD@mu_b
# params_FD@selectivity
# params_FD@catchability
# params_FD@interaction

sim_FD_bmsy <- project(params_FD, effort = 0, dt = dt, fleetDynamics = TRUE, multiFleet = FALSE, management = TRUE, price = df_price_new, cost = df_cost3, diet_steps = 2, ke = ke_fleet, initial_n = initial_n, initial_n_pp = initial_n_pp, initial_n_bb = initial_n_bb, initial_effort = initial_effort, scaling_price = scaling_price, Blevel_management = "Bmsy")

# fast compare catches 
compareTrends(sim_fitted,sim_FD = sim_FD_bmsy, fleetDynamics = TRUE,type = "yield",yieldObs_timeVariant,ssbObs,rescale=3,areaEco)$plotYield_sp
compareTrends(sim_fitted,sim_FD = sim_FD_bmsy, fleetDynamics = TRUE,type = "yield",yieldObs_timeVariant,ssbObs,rescale=0,areaEco)$plotYield_fl
compareTrends(sim_fitted,sim_FD = sim_FD_bmsy, fleetDynamics = TRUE,type = "yield",yieldObs_timeVariant,ssbObs,rescale=0,areaEco)$plotEffort_fl

# compare profit and effort (to figure out ke)
sim_FD_bmsy@effortOut
sim_FD_bmsy@profit
sim_FD_bmsy@BioOut[[22]]

# see catch by species and fleet to adjust Q can calibrate df_target better? 


# # compared with other communities
# plot(sim_calibrated)
# plot(sim_fitted)
# plot_CN(sim_FD_bmsy)
# plotFleet(sim_FD_bmsy)
# 
# # diet
# dim(sim_FD_bmsy@diet_comp) # predator X size X prey X prey size
# plotDietComp(sim_FD_bmsy)$p
# image(sim_FD_bmsy@diet_comp[19,,9,])
# 
# # growth
# df_param[,c(1,5,8)]
# df_param$max_age<-c(4,7,10,40,25,44,30,40,12,18,22,100,25,23,16,30,15,16,55)
# spp = as.character(df_param[19,1])
# max_age = df_param[19,"max_age"]
# plotGrowthCurves(sim_FD_bmsy, species = spp, max_age = max_age)

```

#-----------------------------------------
# save data
#----------------------------------------------

```{r}

# save.image(file = "/Users/nov017/Dropbox/Mizer-fleet_extension/data/FDData_opn3.RData") # was FDData_Nov2.RData or FDData_Nov.RData if using SEAmodel_opn2.RData as input and Tune Q opn2 

```

#-----------------------------------------
# plot - catch by species and fleet *move to DataFunction?*
#---------------------------------------------- 

```{r}

# modelled catch by species AND fleet
trial<-compareTrends(sim_fitted,sim_FD = sim_FD_bmsy, fleetDynamics = TRUE,type = "yield",yieldObs_timeVariant,ssbObs,rescale=0,areaEco)$trial
trial<-as.data.frame.table(trial, responseName = "yield")
colnames(trial)<-c("year", "species","fleet", "yield_tonnes")

# observed catch by species and fleet. This is as per code in SEA_FleetParam.Rmd line 1647 to calculate datValidationYieldSpp which theh bocame yieldObs_timeVariant in createFmort() in DataFunction.r - thus follwong same protocoll as per all observed data for validation 
datValidationYieldSppFl<-df_log_spp %>%
  filter(metier %in% df_main_metier, SPC_NAME %in% df_param$species) %>% 
  group_by(SPC_NAME, metier, YEAR) %>% 
  dplyr::summarise(catchComm = sum(TOT_CATCH_KG, na.rm=TRUE)/1e3) %>% 
  `colnames<-`(c("species","fleet","year","yield_tonnes")) %>% 
  mutate(fleet = case_when(fleet == "GHAT - Southern Shark Gillnet" ~ "SSG",
                           fleet == "South East Trawl Fishery - Danish Seine" ~ "SED",
                           fleet == "South East Trawl Fishery - Otter trawl deepSlope" ~ "SET-DS",
                           fleet == "South East Trawl Fishery - Otter trawl shelf" ~ "SET-SH",
                           fleet == "South East Trawl Fishery - Otter trawl upperSlope" ~ "SET-US")) 

# modelled and observed together
# NOTE: you added catches and calcualted Fmort according to these catches for trachurus. Here they are missing but Q=1 for tracurus and these fleets.  
datValidationYieldSppFl$color<-"observed"
trial$color <- "modelled_FD"
trial$year<-as.numeric(as.character(trial$year))
trial$species<-as.character(trial$species)
trial$fleet<-as.character(trial$fleet)
yieldData_sp_fl<-merge(trial,datValidationYieldSppFl, all =TRUE ) 
yieldData_sp_fl<-yieldData_sp_fl%>% 
  filter(year >= 2006) %>% 
  left_join(df_param[,c(1,2)])

# plot modelled vs observed
p <- ggplot(yieldData_sp_fl) + 
  geom_line(aes(x=year, y = yield_tonnes, colour=spCommon), size=1) +
  theme_bw() +
  facet_grid(fleet~color, scale ="free")

```

# last updates: 
I changed costs from g to opn and nothing changed in term of trends, but they make profits negative - keep g 
I changed management rule to decrease effort in proportion to biomass of target (fixed a bug) - it improved trends 
I need to reconsider the scale of ke so that changes in profits are reflected in changes in effort and as per units as discussed with Beth - values of ke ~ 100000 make changes in effort due to profit visible 
I still need to add profits to the data and plot? 

# Other importnatn notes 
from SEAmodel_run.Rmd: gummy sharks and OR abudnances are too high?! you have increased them to fix catches. You could have increased Fmort instaed of r_max.

#-----------------------------------------
# plot - catch and effort by species or fleet
#---------------------------------------------- 

```{r}

plotBio_sp<-plotBiomass_CN(sim_fitted,sim_FD_bmsy, df_param, rescale = 0)$p 
BioData<-plotBiomass_CN(sim_fitted,sim_FD_bmsy, df_param, rescale = 0)$BioData
colnames(BioData)<-c("year", "species","bio_tonnes","type","common")

prova<-BioData %>% 
  select(-species) %>% 
  filter(type == "modelled_FD") %>% 
  group_by(common, type) %>% 
  dplyr::summarise(value = mean(bio_tonnes))
as.data.frame(prova[order(-prova$value),])

plotSSB_sp<-compareTrends(sim_fitted,sim_FD = sim_FD_bmsy, fleetDynamics = TRUE,type = "SSB",yieldObs_timeVariant,ssbObs,rescale=0,areaEco)$plotYield_sp 
SSBData<-compareTrends(sim_fitted,sim_FD = sim_FD_bmsy, fleetDynamics = TRUE,type = "SSB",yieldObs_timeVariant,ssbObs,rescale=0,areaEco)$DataPlotYield
colnames(SSBData)<-c("year", "species","ssb_tonnes","type","common")

plotYield_sp_rescaled<-compareTrends(sim_fitted,sim_FD = sim_FD_bmsy, fleetDynamics = TRUE,type = "yield",yieldObs_timeVariant,ssbObs,rescale=3,areaEco)$plotYield_sp 
plotYield_sp_rescaled2<-compareTrends(sim_fitted,sim_FD = NA, fleetDynamics = FALSE,type = "yield",yieldObs_timeVariant,ssbObs,rescale=3,areaEco)$plotYield_sp 

# whcih colors are used in this plots? 
ggplot_build(plotYield_sp_rescaled)$data
# change colurs accordingly 
plotYield_sp_rescaled2<- plotYield_sp_rescaled2+
  scale_color_manual(values=c("#440154FF", "#21908CFF"))

plotYield_sp_raw<-compareTrends(sim_fitted,sim_FD = sim_FD_bmsy, fleetDynamics = TRUE,type = "yield",yieldObs_timeVariant,ssbObs,rescale=0,areaEco)$plotYield_sp 
yieldData<-compareTrends(sim_fitted,sim_FD = sim_FD_bmsy, fleetDynamics = TRUE,type = "yield",yieldObs_timeVariant,ssbObs,rescale=0,areaEco)$DataPlotYield
colnames(yieldData)<-c("year", "species","yield_tonnes","type","common")

yieldData_spp_fleet<-yieldData_sp_fl # being added to the outputs 

plotYield_fl<-compareTrends(sim_fitted,sim_FD = sim_FD_bmsy, fleetDynamics = TRUE,type = "yield",yieldObs_timeVariant,ssbObs,rescale=0,areaEco)$plotYield_fl
yieldData_fleet<-compareTrends(sim_fitted,sim_FD = sim_FD_bmsy, fleetDynamics = TRUE,type = "yield",yieldObs_timeVariant,ssbObs,rescale=0,areaEco)$DataPlotYield_fl 
colnames(yieldData_fleet)<-c("year", "fleet","yield_tonnes","type")

plotEffort_fl<-compareTrends(sim_fitted,sim_FD = sim_FD_bmsy, fleetDynamics = TRUE,type = "yield",yieldObs_timeVariant,ssbObs,rescale=0,areaEco)$plotEffort_fl
effortData<-compareTrends(sim_fitted,sim_FD = sim_FD_bmsy, fleetDynamics = TRUE,type = "yield",yieldObs_timeVariant,ssbObs,rescale=0,areaEco)$DataPlotEffort_fl 
colnames(effortData)<-c("year", "fleet","effort_opn","type")

# Plot effort and catch by fleet together
a<-effortData
b<-yieldData_fleet

colnames(a)<-c("year", "fleet", "EFFORT", "color")
colnames(b)<-c("year", "fleet", "YIELD", "color")
temp<-merge(a, b, all = TRUE)
temp<-temp %>% 
  gather("type", "value", -c(year, fleet, color))

scaleFUN <- function(x) sprintf("%.0f", x)

plotEffortCatch_fl <- ggplot(temp, aes(x=year, y = value, colour=color)) + 
  geom_line(aes(x=year, y = value, colour=color), size=1) +    
  scale_x_continuous(labels = scaleFUN, name = "Year") +
  theme_bw() +
  theme(legend.title = element_blank(),
        text = element_text(size=12),
        legend.text=element_text(size=12),
        axis.title.y = element_text(size=12, vjust=0.4),
        axis.title.x = element_text(size=12, vjust=0.3),
        axis.text.y = element_text(size=10, hjust=0.5),
        axis.text.x = element_text(size=10, angle = 90, hjust=0.5),
        panel.grid.major = element_blank(),
        strip.background = element_rect(colour="black", fill= NA)) +
  scale_y_continuous(name = "tonnes                    operations")+
  facet_grid(vars(type), vars(fleet), scales="free_y")

```

#-----------------------------------------
# save plots and csv
#----------------------------------------------

```{r}

library(patchwork)

# # plots
# setwd("/Users/nov017/dataXBeth/SEA_sizespectrum_outputs") # need to change directory.... 
# 
# tiff("plotSSB_sp.tiff", height=6, width=9, units ='in', res=300)
# plotSSB_sp 
# dev.off()
# 
# tiff("plotYield_sp_rescaled_FLT.tiff", height=6, width=9, units ='in', res=300)
# plotYield_sp_rescaled
# dev.off()
# 
# tiff("plotYield_sp_rescaled_no_FD.tiff", height=6, width=9, units ='in', res=300)
# plotYield_sp_rescaled2
# dev.off()
# 
# tiff("plotYield_sp_raw_FLT.tiff", height=6, width=9, units ='in', res=300)
# plotYield_sp_raw
# dev.off()
# 
# tiff("catch_Comp.tiff", height=8, width=9, units ='in', res=300)
# p
# dev.off()
# 
# tiff("plotYield_fl.tiff", height=4, width=9, units ='in', res=300)
# plotYield_fl
# dev.off()
# 
# tiff("plotEffort_fl.tiff", height=4, width=9, units ='in', res=300)
# plotEffort_fl
# dev.off()

# tiff("/Users/nov017/Desktop/plot_fleet.tiff", height=4, width=9, units ='in', res=300)
# plotEffortCatch_fl
# dev.off()

# # csv data
# write.csv(BioData, "BioData.csv",row.names=FALSE)
# write.csv(SSBData, "SSBData.csv", row.names=FALSE)
# write.csv(yieldData, "yieldData.csv", row.names=FALSE)
# write.csv(yieldData_spp_fleet, "yieldData_spp_fleet.csv", row.names=FALSE)
# write.csv(yieldData_fleet, "yieldData_fleet.csv", row.names=FALSE)
# write.csv(effortData, "effortData.csv", row.names=FALSE)

```

#-----------------------------------------
# Shiny *Delete?*
#----------------------------------------------

```{r}

sim = sim_fitted
df_param = df_param
interaction = theta
kappa = kappa
kappa_ben = kappa_ben
kappa_alg = kappa_alg 
w_pp_cutoff = w_pp_cutoff 
min_w_bb = min_w_bb
w_bb_cutoff = w_bb_cutoff
fleetDynamics = TRUE
selectivity_params = df_selParam_new
catchability = df_target_bmsy
target = df_target_bmsy
effort = 0
dt = 0.5 
management = TRUE
price = df_price_new
cost = df_cost3
diet_steps = 0
ke = ke_fleet
initial_n = initial_n
initial_n_pp = initial_n_pp
initial_n_bb = initial_n_bb
initial_effort = initial_effort
scaling_price = scaling_price
Blevel_management = "Bmsy"

type = "yield"
rescale = 0

# source("/Users/nov017/Dropbox/Mizer-fleet/R/SEA_Shiny.R")
# fn_shiny_FD(df_param, theta, kappa, kappa_ben, kappa_alg, w_pp_cutoff, min_w_bb, w_bb_cutoff, fleetDynamics, selectivity_params, catchability, target, effort, dt, management, price, cost, diet_steps, ke, initial_n, initial_n_pp, initial_n_bb, initial_effort, scaling_price, Blevel_management, sim, type, yieldObs_timeVariant,ssbObs,rescale, areaEco)

# arrivata qui - something is wromng with Shiny as it does not reproduce the same trends when changing target values.... need to re-check adn re-run 

# to adjust 
# SSB option is different from fleetDynamics = TRUE and FALSE (when FALSE you ahev problems with fleet plots)
# rescaling options need to be rechecked for FD = TRUE
# add profitability values 

# to explore: 
# starting effort values for all fleets - in Shiny 
# ke for all fleets 
# Q for all species - in Shiny 
# management rule 

```

